О множествах точек на плоскости с целочисленными расстояниями

### 2018-09-23 vmmsh-2018/blg.tex
[vmmsh] Bibiliography - rather working

\textsl{Erdös} \textsl{P.} Integral distances // Bulletin of the

@@

Integral distances // Bulletin of the American Mathematical

@@

\textsl{Solymosi} \textsl{J.} Note on integral distances //

@@

Equations // The American Mathematical Monthly. — 1915. —

@@

// Discrete \& Computational

@@

integral distances between points in the plane // Discrete \&

@@

the minimum diameter of integral point sets // arXiv preprint

@@

Эрдёша // Современные методы теории краевых задач :

@@

approach // Discrete Applied Mathematics. — 2002. — Т. 122,

@@

in a square problem // Discrete Applied Mathematics. — 2013. —

@@

a unit square" problems // SIAM Journal on Optimization. —

@@

плоскости с целочисленными расстояниями // Математическое

@@

отыскания // Некоторые вопросы анализа, алгебры, геометрии

@@

// Discrete Applied Mathematics. — 2006. —

@@

sets in // arXiv preprint math/0511704. — 2005.

@@

Diameters of integral point sets // Colloquia Mathematica

@@

$k$-dimensionalen euklidischen Raum // Abh. Braunschw. Wiss.

@@

diameter of integral point sets // Australasian Journal of

@@

Point sets with small integral distances // Applied geometry and

@@

\textsl{Harborth} \textsl{H.} Integral distances in point sets //

@@

the minimum diameter of plane integral point sets // arXiv

@@

расстояниями // Математические заметки. — 2016. — Т. 100,

@@

integral heptagons, no three points on a line, no four on a circle //

@@

for $1 < n < 7$ // Mathematics of Computation. — 1989. — Т. 53,

@@

Constructing 7-clusters / S. Kurz [и др.] // arXiv preprint

@@

integral distances? // The American Mathematical Monthly. —

@@

\textsl{Erdös} \textsl{P.} On sets of distances of n points //

@@

Erdos distinct distances problem in the plane // Annals of

>>>>

\textsl{Erdös} \textsl{P.} Integral distances /\!/ Bulletin of the

@@

Integral distances /\!/ Bulletin of the American Mathematical

@@

\textsl{Solymosi} \textsl{J.} Note on integral distances /\!/

@@

Equations /\!/ The American Mathematical Monthly. — 1915. —

@@

/\!/ Discrete \& Computational Geometry

@@

integral distances between points in the plane /\!/ Discrete \&

@@

the minimum diameter of integral point sets /\!/ arXiv preprint

@@

Эрдёша /\!/ Современные методы теории краевых задач :

@@

approach /\!/ Discrete Applied Mathematics. — 2002. — Т. 122,

@@

in a square problem /\!/ Discrete Applied Mathematics. — 2013. —

@@

a unit square" problems /\!/ SIAM Journal on Optimization. —

@@

плоскости с целочисленными расстояниями /\!/ Математическое

@@

отыскания /\!/ Некоторые вопросы анализа, алгебры, геометрии

@@

/\!/ Discrete Applied Mathematics. — 2006. —

@@

sets in /\!/ arXiv preprint math/0511704. — 2005.

@@

Diameters of integral point sets /\!/ Colloquia Mathematica

@@

$k$-dimensionalen euklidischen Raum /\!/ Abh. Braunschw. Wiss.

@@

diameter of integral point sets /\!/ Australasian Journal of

@@

Point sets with small integral distances /\!/ Applied geometry and

@@

\textsl{Harborth} \textsl{H.} Integral distances in point sets /\!/

@@

the minimum diameter of plane integral point sets /\!/ arXiv

@@

расстояниями /\!/ Математические заметки. — 2016. — Т. 100,

@@

integral heptagons, no three points on a line, no four on a circle /\!/

@@

for $1 < n < 7$ /\!/ Mathematics of Computation. — 1989. — Т. 53,

@@

Constructing 7-clusters / S. Kurz [и др.] /\!/ arXiv preprint

@@

integral distances? /\!/ The American Mathematical Monthly. —

@@

\textsl{Erdös} \textsl{P.} On sets of distances of n points /\!/

@@

Erdos distinct distances problem in the plane /\!/ Annals of
